Self Regulation Ontology Retest Data Report

### 2017-11-04 code/SRO_Report.Rmd
ordered the variance breakdown plot

```{r warning=FALSE, message=FALSE}
p1 = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  gather(key, value, -dv, -task) %>%
  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var),
         var=gsub(".ReflogTr", "", var),
         var=gsub(".logTr", "", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="task",
         !grepl("EZ|hddm", dv))%>%
  ggplot(aes(x=var, y=value, fill=key))+
  geom_bar(stat='identity', alpha = 0.75)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"),
                     h=c(100,500))+
  ylab("")+
  xlab("")

p2 = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  gather(key, value, -dv, -task) %>%
  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="survey")%>%
  ggplot(aes(x=var, y=value, fill=key))+
  geom_bar(stat='identity', alpha = 0.75)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"),
                    h=c(100,500))+
  ylab("")+
  xlab("")

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(p1)

>>>>

```{r warning=FALSE, message=FALSE}
tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  # gather(key, value, -dv, -task) %>%
  mutate(#key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var),
         var=gsub(".ReflogTr", "", var),
         var=gsub(".logTr", "", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="task",
         !grepl("EZ|hddm", dv))%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p1 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75, color='#00BFC4')+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

tmp = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  # gather(key, value, -dv, -task) %>%
  mutate(#key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  arrange(task_group, var_subs_pct) %>%
  mutate(rank = row_number()) %>%
  arrange(task, task_group, rank) %>%
  gather(key, value, -dv, -task_group, -var, -task, -rank) %>%
  ungroup()%>%
  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var),
         var=gsub(".ReflogTr", "", var),
         var=gsub(".logTr", "", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="survey")%>%
  arrange(task_group, rank)
labels = tmp %>%
  distinct(dv, .keep_all=T)

p2 <- tmp %>%
  ggplot(aes(x=factor(rank), y=value, fill=factor(key, levels = c("var_resid_pct", "var_ind_pct", "var_subs_pct"))))+
  geom_bar(stat='identity', alpha = 0.75)+
  geom_bar(stat='identity', color='#F8766D', show.legend=FALSE)+
  scale_x_discrete(breaks = labels$rank,
                       labels = labels$var)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey85"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                      labels = c("Variance between individuals",
                                 "Variance between sessions",
                                 "Error variance"),
                  values=c("grey65", "grey45", "grey25"))+
  ylab("")+
  xlab("")

mylegend<-g_legend(p2)
